Lattice Boltzmann simulations of magnetically responsive\\ ellipsoidal particle stabilized emulsions

### 2025-03-21 chapters/paper2.tex
Changes 1. Addressed some image sizes and phrasing consistency
Draft 1 complete
Removed some overhang from images in paper2.tex
Changed I to we in results chapters

Bijels have proposed applications as soft matter based material templates, drug delivery vectors and separations systems. The materials 
performance in each application is dependent upon the microstructure of the bijel template. Many of the applications listed above benefit 
from stimuli response, allowing for in-situ microstructure tuning to offer reversible modifications of material permeability. In this section, I analyze
whether stimuli responsive bijels provide access to reversible structural modifications.

We begin our investigation by characterizing the microstructure changes observed on bijels stabilized with prolate ellipsoids with a 
particle volume fraction of $\phi_p = 0.1$. We only focus on one system here as the mechanism for stimuli response shown in Aim 1 is identical
for both systems. Therefore we expect that the qualitative trends between prolate and oblate particles will be matched. I select prolate particles
as they are more readily synthesizable in experiments.

I apply a constant magnetic field of $\bar{B}_z = 0.2$ onto bijels that were simulated 
with no magnetic field. Once the microstructure has reached its new state, I ramp up the magnetic field to $\bar{B}_z = 0.5$ and 
finally $\bar{B}_z = 1$. I then apply the opposite procedure to reduce the applied field strength, resulting in a magnetic field 
ramp of $\bar{B}_z: 0 \rightarrow 0.2 \rightarrow 0.5 \rightarrow 1 \rightarrow 0.5 \rightarrow 0.2 \rightarrow 0$. I characterize the 
microstructure changes observed through calculating the domain size, defined as the first moment of the spherically averaged structure factor. 
I calculate the hysteresis 
curve by selecting the domain size at the final timestep of each magnetic field change. I then plot these domain sizes against the magnetic field 
applied to obtain them and split them in the descending and ascending magnetic field directions to demonstrate the differences observed. I plot 
these results in Figure \ref{fig:hysteresis_curve}

\begin{figure} 
    \centering 
    \includegraphics[scale=0.5]{../figures/results/paper2/hysteresis_curve.png} 
    \caption{Plot of the hysteresis curve of a bijel stabilized by magnetically responsive prolate particles. I observe that the domain size increases as we 
    increase the applied magnetic field strength. However, upon decrease of the applied field strength the microstructure does not return to its previous value,
    demonstrating microstructure hysteresis.} 
    \label{fig:hysteresis_curve} 
\end{figure}

@@

This behavior is also observed in past work investigating the shape deformation of particle stabilized emulsions under 
electric fields. \cite{cui_stabilizing_2013} Cui et al. demonstrated that the particles unjammed and rejammed into a new kinetically arrested state resulting in
the droplet being elongated in the direction of the applied field. This suggests that the particles at the interface of magnetically responsive bijels are in
in a kinetically trapped configuration. Cui et al. used spherical particles in their emulsion response experiments while we use ellipsoidal particles. Additionally,
we also observe in Figure \ref{fig:hysteresis_curve} that the response of the bijel is dependent upon the field strength applied.
In the following sections, I investigate the impact of magnetic field strength and the initial ordering of the particle monolayer on the observed stimuli response.

@@

From the results in Figure \ref{fig:hysteresis_curve}, I show that the domain size change is dependent upon the applied magnetic field. As porous materials templates,
the microstructure of the material is of interest as it controls the performance of the material. Additionally, in many of the proposed stimuli responsive applications
for bijels, the timescales of response is important to characterize and would also provide a mechanistic understanding of the reasons why the microstructure changes 
occur. In this section, I analyze the structural response of bijels by assessing the response of bijels stabilized by particles with volume fraction of 
$\phi_p = 0.1$ simulated under no applied field to an applied field in the range $\bar{B} = 0, 0.2, 0.5, 1$. I begin my investigation by visualizing the structure before 
and after the application of magnetic fields.

@@

In Figure \ref{fig:microstructure_viz-field_on} I show representative snapshots of the bijel at the initial and final timestep with $\bar{B}_z = 0$ and $\bar{B}_z = 1$. 
Upon application of the field, particles align to the direction of the field. As the particles orient to the field, they disrupt the packing of particles at
the interface. This causes domain coarsening as the particles rearrange into new positions before rejamming in place once the interfacial
area and particle cross sectional area match. Domain coarsening observed in the figure can be explained through the ordering of particles at the interface, causing a 
reduction in the available area that the particles have for stabilization. To characterize the length scale of the microstructure upon application of the magnetic field,
I calculate the domain size. To correlate the microstructure evolution to the ordering of the particle monolayer to the magnetic field, I overlay the time evolution of the
nematic order parameter on the domain size. \cite{veerman_phase_1992}

@@

I normalized the domain size results by the volume equivalent sphere radius, $R = 7.9$ in Figure \ref{fig:domain_size-field_on} The results indicate that upon 
applying a magnetic field to a bijel initially formed without one, the final average domain size increases by up to 5.2\% and 2.5\% for oblate and 
prolate particle stabilized bijels respectively. The domain coarsening is initially slow, before accelerating rapidly and finally reaching a maximum where it plateaus. 
Additionally, in the absence of an external field, domain coarsening occurs for both particle morphologies. However, the results
for oblate particles with a magnetic field is attributed to coalescence of domains rather than magnetic field driven ordering of the particles.

@@

Precise characterization of the anisotropic microstructure is essential for the tailored design of application-specific porous materials. To
quantify the characteristic length scales in each Cartesian direction, I compute the second-moment-derived structure factor. \cite{jansen_bijels_2011} 
I also calculate the tortuosity  in each cartesian direction. I make a further
refinement simplifying the domain sizes to directions parallel and orthogonal to the magnetic field. These result in the length scales and
their associated calculation, $L_{\parallel} = L_{z}$ and $L_{\perp} = \frac{L_x + L_y}{2}$. The same simplification
with the directional tortuosities is also performed.

Tortuosity has been defined using the geometric, diffusional and hydraulic tortuosities. The tortuosity calculated here is
the diffusional tortuosity, $\tau = \frac{D}{D_{eff}}$ which characterizes the ratio between the free diffusion of a tracer and the
effective diffusion of a tracer in the material. I plot the directional second moment derived length scales and tortuosity in
Figure \ref{fig:domain_size_aniso-field_on}.

@@

From Figure \ref{fig:domain_size_aniso-field_on}, domain size anisotropy is observed upon application of the field for both
particle morphologies. I also see some domain anisotropy with no applied field, which increases upon application of the magnetic field.
The directional domain sizes, $L_{\perp}$ and $L_{\parallel}$ increase by 73\% and 7\%\ respectively for oblate particles and
10\% and 44\% respectively for oblate particles. The axes that coarsens the most is consistent with past work, explained through the
directions particles reorient in response to the applied magnetic field. As particles unjam and rejam at the interface due to reorientating 
to the magnetic field, they adopt direction specific surface coverages which manifest as anistropic domains upon jamming. In Figure 
\ref{fig:domain_size_aniso-field_on}, we demonstrate that the application of the magnetic field changes the domain size.

The tortuosity of the bijel is initially around $\tau \approx 1.5$, consistent with simulations of the diffusive tortuosities of gyroid structures using 
Lattice Boltzmann simulations. \cite{luo_macroscopic_2020} Upon application of the field, $\tau_{\perp}$ slightly decreases while $\tau_{\parallel}$
increases. In Chapter \ref{chapter:aim1}, I characterized that increasing the domain size decreases the tortuosity. \cite{karthikeyan_formation_2024} This
observation is in line with the domain size changes observed in Figure \ref{fig:domain_size_aniso-field_on}. The results show that the
tortuosity of the bijel is noticeably affected by the application of magnetic fields. This data suggests that magnetic fields applied onto
bijels stabilized with ellipsoidal particles undergo domain anisotropy upon application of magnetic fields. However the particle morphology,
specifically its axis of symmetry, affect the direction that the domain anisotropy is characterized.

Next, I return to investigate the time gap between the average domain size increase and the nematic order parameter. This result suggests that the dynamics 
of the system at higher magnetic field strengths are dependent upon other factors that vary upon application of the magnetic field. In this system, these factors
would arise from capillary forces with the interface or steric interactions with other particles at the interface, slowing down the dynamics of the system.
To understand this phenomena, I focus on the dynamics of the particle monolayer. First, I visualize the particle monolayer of the bijels stabilized with prolate 
ellipsoids at the initial and final configuration before and after application of a magnetic field.

@@

In Figure \ref{fig:particle_viz-field_on}, I see the initial configuration of particles at the monolayer show that the orientations are random and that the 
particles tend to lie flat on the interface. However, upon application of the magnetic field the particles orient to the field direction. With no applied field,
I see that the orientations and positions of the particles vary slightly for both ellipsoidal particle morphologies. This effect is due steric effects between particles,
as identified in Gunther et al. \cite{gunther_timescales_2014} I observe that for bijels stabilized by prolate ellipsoids, we see the adoption of orientational order
to the magnetic field and qualitatively different particle arrangements on the interface. These indicate that the interfacial capillary forces or steric interactions 
with other particles differ upon application of the magnetic field. The particles would prefer to lie flat on the interface to minimize the interfacial energy of 
adsorption onto the interface. Changes in the local arrangement arise from the unjamming and rejamming process upon application of the magnetic field. These differences 
in the orientational and interfacial ordering can be characterized to understand how each respective interaction force changes as a function of time.

Bresme and Faraudo and Davies investigating the reorientation of particles at interfaces under magnetic fields have shown that a critical magnetic field exists, 
above which the particle orients to the field and below which the particle orientation is a function of the capillary force and magnetic field derived force. 
\cite{davies_interface_2014} \cite{bresme_orientational_2007} Particle adsorption into the interface with microparticles have also been shown to be irreversible due 
to the high adsorption energy. Upon particle reorientation, the microstructure change can be driven solely through particle unjamming and re-jamming, or it can be 
driven through the particles dragging the interface during this process. The mechanism of unjamming and re-jamming can be investigated using the average interfacial 
angle, $\langle \psi \rangle$ and the local ordering of the particles characterized with  $\langle Q6 \rangle$ Past work has identified that local crystallization 
of colloidal supercooled fluids takes place at \(\langle Q6 \rangle = 0.38\). \cite{toxvaerd_role_2020} Past investigations into the rheology of bijels have revealed
that bijels are colloidal glasses percolating in 3D space. \cite{ching_bijel_2022} However, application of a magnetic field results in reorientation of particles on
the interface that can temporarily reduce the interfacial coverage of the particles on the interface, temporarily making the particle monolayer more liquid-like
than amorphous. \cite{hunter_physics_2012} Using this approximation, I can use the local crystallization result shown in Toxvaerd.

\begin{figure} 
\centering 
\includegraphics[scale=0.3]{../figures/results/paper2/interface_angle-nint-field_on.png} 
\caption{Plots of the interface angle $(\langle \psi \rangle)$ and six fold Steinhardt order parameter $(\langle Q6 \rangle)$ on the left and right respectively, 
         versus time for bijels stabilized with oblate and prolate ellipsoids on the top and bottom rows respectively. We demonstrate that upon application 
         of a magnetic field, the behavior of $(\langle \psi \rangle)$ and $(\langle Q6 \rangle)$ differ significantly between oblate and prolate ellipsoids 
         indicating that the dynamics for both particle morphologies differ. We also observe magnetic field dependence in each property for both particle types, 
         suggesting that these changes are driven primarily through the change in the applied field strength.} 
\label{fig:interface_angle-nint-field_on} 
\end{figure}

From Figure \ref{fig:interface_angle-nint-field_on}, we identify that prolate and oblate particles respond differently at the interface. For
bijels stabilized by oblate ellipsoids, I characterize an increase in $\langle \psi \rangle$ from an initial value of $19 ^{\circ}$,
before it reduces slightly and begins to increase once again. The initial starting value of $\langle \psi \rangle$ indicates the
particles are lying close to flat on the interface, before they begin to tilt out of the interface when the magnetic field is applied. Then,
$\langle \psi \rangle$ plateaus as the interface begins to move in response to the tilting particle at the interface. This is caused by the
large adsorption energy of the particles at the interface of the bijel, caused by high surface tension. Finally, the particles jam in place,
locking the interface at an angle to the particle. We see the rate of increase in $\langle \psi \rangle$ at early stages and the time spent
in the plateau increase with a larger applied magnetic field. The final angle at the interface is also dependent upon the applied field
strength.

When analyzing $\langle \psi \rangle$ for bijels stabilized by prolate particles, this behavior can also be observed. $\langle \psi \rangle$
begins at $10 ^{\circ}$.We see $\langle \psi \rangle$ increases, before plateauing and slowly decreasing. The initial peak height and rate of increase in 
$\langle \psi \rangle$ is field dependent, although given the small decrease in $\langle \psi \rangle$ it is unclear if the final value of this parameter 
is field dependent for bijels stabilized with prolate particles. The changes in $\langle \psi \rangle$ for bijels stabilized with prolate particles are 
small compared to bijels stabilized with oblate particles. We visualize this process by color coding snapshots of the particle monolayer at the initial
and final timesteps of bijels stabilized by prolate particles with a field strength of $\bar{B} = 1$ applied.

@@

From the visualizations in Figure \ref{fig:psi_field_on_visualize}, the particles lie mostly flat on the interface at the initial timestep. Upon application of a field 
strength of $\bar{B} = 1$, the final state of the monolayer is particle morphology dependent. Oblate particles tend to flip on the interface into a metastable state where
the interface covered by each particle is done with the $R_p$ and $R_o$ compared to its lowest energy state where it lies flat with radii $R_o$. The particle monolayer
of bijels stabilized by prolate particles tilt out of the interface with no metastable configurations observed. This effect explains the trends seen in $\langle \psi \rangle$
at long times for both particle morphologies. This particle flipping on the interface affects the way the particles can arrange on the interface, like what I 
characterized In Figure \ref{fig:rdf}. This change in local ordering can be quantified using $\langle Q6 \rangle$.

From Figure \ref{fig:interface_angle-nint-field_on} the dynamics of $\langle Q6 \rangle$ are particle morphology specific but can be split into three sections for 
both particle morphologies. Characterizing the time evolution of $\langle Q6 \rangle$ for oblate particles, I see a decrease upon application of the magnetic field, 
followed by a plateau and finally a gradual increase before jamming takes place, seen as a significant decrease in the rate of chang to $\langle Q6 \rangle$.
These results indicate that the ordering of the particles is reduced by the applied magnetic field, before a
restoration of some of the pre-existing order. The final values of $\langle Q6 \rangle$ are magnetic field dependent, with a stronger
magnetic field having a lower final $\langle Q6 \rangle$ value indicating that either the ordering of particles influence the angle at
the interface or vice versa.

I observe that for bijels stabilized by prolate particles, the interface ordering of the particles increases as a
function of the applied field strength. The first phase of the evolution of $\langle Q6 \rangle$ sees some growth in $\langle Q6 \rangle$ before 
increasing dramatically and plateauing as jamming takes place. The length of time of the initial plateau and growth regions are negatively and
positively correlated to the applied magnetic field strength. Upon application of the magnetic field, $\langle Q6 \rangle > 0.38$ in all cases. Approximating
the particle monolayer as a colloidal glass that underwent a glass transition, the monolayer can be said to undergo a local crystallation event when 
$\langle Q6 \rangle > 0.38$. \cite{toxvaerd_role_2020}

Thus far, three particle based phenomena have been characterized; the orientation of the particle to the magnetic field, the interface and the local 
arrangement of the particles on the interface. I can calculate a timescale for each factor from the plots of each of these properties.
The nematic order parameter $S$ represents the ordering of
particles to an average direction, which in the case of the application
of a magnetic field, is the field direction. Therefore, a timescale
reliant on the nematic order parameter would represent a timescale of
response rate limited to the response to the magnetic field, which
indicates a particle-field orientation dependence. I name this
timescale $\tau_S$. When applying a field to a bijel system with a
randomly oriented particle monolayer, the most significant transition
point is the isotropic to nematic transition or when $S \geq 0.3$. We
define $\tau_S$ as the the isotropic to nematic transition point.

I can also do the same for $\langle \psi \rangle$ and
$\langle Q6 \rangle$. A timescale derived from
$\langle \psi \rangle$ named $\tau_{\langle \psi \rangle}$
represents the capillary timescale between the interface and the
particle. Given the shape of the plot, we assign the
$\tau_{\langle \psi \rangle}$ to be the time when the first minimum of
$\langle \psi \rangle$ is observed for prolate particles and the first
maximum for oblate particles. A timescale derived from
$\langle Q6 \rangle$, named $\tau_{\langle Q6 \rangle}$ is also
calculated which represents a timescale of local particle rearrangement.
We define $\tau_{\langle Q6 \rangle}$ as the time when
\(\langle Q6 \rangle \geq 0.38\) for prolate particles and the global
minimum of $\tau_{\langle Q6 \rangle}$ for the oblate particles. I
omit \(\bar{B} = 0\) as previous results have identified the domain size
changes observed there. I then plot the average domain size $L$
against time rescaled with these three timescales in Figure
\ref{fig:domain_size-field_on-scaled}.

@@

The right plot demonstrates the domain size change after rescaling time
with $\tau_{\langle Q6 \rangle}$ all plots collapse onto a single line and 
the domain size transition also begins at
$\frac{t}{\tau_{\langle Q6 \rangle}} = 1$. The latter point
demonstrates that the dynamics for the structural response of randomly
oriented particles are controlled by the local particle rearrangement at
the interface rather than the orientation of the particle to the
magnetic field. As the dynamics of both particle morphologies are well described
using the particle steric effects timescale, denoted by $\tau_{\langle Q6 \rangle}$,
I conclude that the dynamics of bijels stabilized by ellipsoidal particles are controlled by
interfacial particle rearrangement at the interface.

@@

Bijels are kinetically stable structures whose properties are dependent
upon the stability of the particle monolayer. Past work into responsive
emulsions have demonstrated resilience to microstructure changes after
application and removal of stimuli even after several months. \cite{cui_stabilizing_2013} However,
in the systems simulated above the particles need not necessarily be in
thermodynamically stable states when jammed upon removal of stimuli as
the particles take up a arrangements not observed when no field is
applied. In this section, I explore how removal of the magnetic field
changes the microstructure of the bijel as a function of the initial
particle order. We use bijels simulated under
$\bar{B}_{template} = 0, 0.2, 0.5, 1$ during formation of the bijel. Once
the microstructure has stabilized, I switch off the magnetic field and
observe the time evolution of the system for $t = 10^5$ timesteps.

>>>>

Bijels have proposed applications as soft matter based material templates, drug delivery vectors and separations systems. The materials 
performance in each application is dependent upon the microstructure of the bijel template. Many of the applications listed above benefit 
from stimuli response, allowing for in-situ microstructure tuning to offer reversible modifications of material permeability. In this section, we analyze
whether stimuli responsive bijels provide access to reversible structural modifications.

We begin our investigation by characterizing the microstructure changes observed on bijels stabilized with prolate ellipsoids with a 
particle volume fraction of $\phi_p = 0.1$. We only focus on one system here as the mechanism for stimuli response shown in Aim 1 is identical
for both systems. Therefore We expect that the qualitative trends between prolate and oblate particles will be matched. We select prolate particles
as they are more readily synthesizable in experiments.

We apply a constant magnetic field of $\bar{B}_z = 0.2$ onto bijels that were simulated 
with no magnetic field. Once the microstructure has reached its new state, we ramp up the magnetic field to $\bar{B}_z = 0.5$ and 
finally $\bar{B}_z = 1$. We then apply the opposite procedure to reduce the applied field strength, resulting in a magnetic field 
ramp of $\bar{B}_z: 0 \rightarrow 0.2 \rightarrow 0.5 \rightarrow 1 \rightarrow 0.5 \rightarrow 0.2 \rightarrow 0$. We characterize the 
microstructure changes observed through calculating the domain size, defined as the first moment of the spherically averaged structure factor. 
We calculate the hysteresis 
curve by selecting the domain size at the final timestep of each magnetic field change. We then plot these domain sizes against the magnetic field 
applied to obtain them and split them in the descending and ascending magnetic field directions to demonstrate the differences observed. We plot 
these results in Figure \ref{fig:hysteresis_curve}

\begin{figure} 
    \centering 
    \includegraphics[scale=0.5]{../figures/results/paper2/hysteresis_curve.png} 
    \caption{Plot of the hysteresis curve of a bijel stabilized by magnetically responsive prolate particles. We observe that the domain size increases as we 
    increase the applied magnetic field strength. However, upon decrease of the applied field strength the microstructure does not return to its previous value,
    demonstrating microstructure hysteresis.} 
    \label{fig:hysteresis_curve} 
\end{figure}

@@

This behavior is also observed in past work investigating the shape deformation of particle stabilized emulsions under 
electric fields. \cite{cui_stabilizing_2013} Cui et al. demonstrated that the particles unjammed and rejammed into a new kinetically arrested state resulting in
the droplet being elongated in the direction of the applied field. This suggests that the particles at the interface of magnetically responsive bijels are in
in a kinetically trapped configuration. Cui et al. used spherical particles in their emulsion response experiments while we use ellipsoidal particles. Additionally,
Figure \ref{fig:hysteresis_curve} shows that the response of the bijel is dependent upon the field strength applied.
In the following sections, we investigate the impact of magnetic field strength and the initial ordering of the particle monolayer on the observed stimuli response.

@@

From the results in Figure \ref{fig:hysteresis_curve}, we show that the domain size change is dependent upon the applied magnetic field. As porous materials templates,
the microstructure of the material is of interest as it controls the performance of the material. Additionally, in many of the proposed stimuli responsive applications
for bijels, the timescales of response is important to characterize and would also provide a mechanistic understanding of the reasons why the microstructure changes 
occur. In this section, we analyze the structural response of bijels by assessing the response of bijels stabilized by particles with volume fraction of 
$\phi_p = 0.1$ simulated under no applied field to an applied field in the range $\bar{B} = 0, 0.2, 0.5, 1$. We begin our investigation by visualizing the structure before 
and after the application of magnetic fields.

@@

In Figure \ref{fig:microstructure_viz-field_on} we show representative snapshots of the bijel at the initial and final timestep with $\bar{B}_z = 0$ and $\bar{B}_z = 1$. 
Upon application of the field, particles align to the direction of the field. As the particles orient to the field, they disrupt the packing of particles at
the interface. This causes domain coarsening as the particles rearrange into new positions before rejamming in place once the interfacial
area and particle cross sectional area match. Domain coarsening observed in the figure can be explained through the ordering of particles at the interface, causing a 
reduction in the available area that the particles have for stabilization. To characterize the length scale of the microstructure upon application of the magnetic field,
we calculate the domain size. To correlate the microstructure evolution to the ordering of the particle monolayer to the magnetic field, we overlay the time evolution of the
nematic order parameter on the domain size. \cite{veerman_phase_1992}

@@

We normalized the domain size results by the volume equivalent sphere radius, $R = 7.9$ in Figure \ref{fig:domain_size-field_on} The results indicate that upon 
applying a magnetic field to a bijel initially formed without one, the final average domain size increases by up to 5.2\% and 2.5\% for oblate and 
prolate particle stabilized bijels respectively. The domain coarsening is initially slow, before accelerating rapidly and finally reaching a maximum where it plateaus. 
Additionally, in the absence of an external field, domain coarsening occurs for both particle morphologies. However, the results
for oblate particles with a magnetic field is attributed to coalescence of domains rather than magnetic field driven ordering of the particles.

@@

Precise characterization of the anisotropic microstructure is essential for the tailored design of application-specific porous materials. To
quantify the characteristic length scales in each Cartesian direction, we compute the second-moment-derived structure factor. \cite{jansen_bijels_2011} 
We make a further refinement simplifying the domain sizes to directions parallel and orthogonal to the magnetic field. These result in the length scales and
their associated calculation, $L_{\parallel} = L_{z}$ and $L_{\perp} = \frac{L_x + L_y}{2}$. The same simplification
with the directional tortuosities is also performed.

Tortuosity has been defined using the geometric, diffusional and hydraulic tortuosities. The tortuosity calculated here is
the diffusional tortuosity, $\tau = \frac{D}{D_{eff}}$ which characterizes the ratio between the free diffusion of a tracer and the
effective diffusion of a tracer in the material. We plot the directional second moment derived length scales and tortuosity in
Figure \ref{fig:domain_size_aniso-field_on}.

@@

From Figure \ref{fig:domain_size_aniso-field_on}, domain size anisotropy is observed upon application of the field for both
particle morphologies. Some domain anisotropy with no applied field is observed, which increases upon application of the magnetic field.
The directional domain sizes, $L_{\perp}$ and $L_{\parallel}$ increase by 73\% and 7\%\ respectively for oblate particles and
10\% and 44\% respectively for oblate particles. The axes that coarsens the most is consistent with past work, explained through the
directions particles reorient in response to the applied magnetic field. As particles unjam and rejam at the interface due to reorientating 
to the magnetic field, they adopt direction specific surface coverages which manifest as anistropic domains upon jamming. In Figure 
\ref{fig:domain_size_aniso-field_on}, we demonstrate that the application of the magnetic field changes the domain size.

The tortuosity of the bijel is initially around $\tau \approx 1.5$, consistent with simulations of the diffusive tortuosities of gyroid structures using 
Lattice Boltzmann simulations. \cite{luo_macroscopic_2020} Upon application of the field, $\tau_{\perp}$ slightly decreases while $\tau_{\parallel}$
increases. In Chapter \ref{chapter:aim1}, we characterized that increasing the domain size decreases the tortuosity. \cite{karthikeyan_formation_2024} This
observation is in line with the domain size changes observed in Figure \ref{fig:domain_size_aniso-field_on}. The results show that the
tortuosity of the bijel is noticeably affected by the application of magnetic fields. This data suggests that magnetic fields applied onto
bijels stabilized with ellipsoidal particles undergo domain anisotropy upon application of magnetic fields. However the particle morphology,
specifically its axis of symmetry, affect the direction that the domain anisotropy is characterized.

Next, we investigate the time gap between the average domain size increase and the nematic order parameter. This result suggests that the dynamics 
of the system at higher magnetic field strengths are dependent upon other factors that vary upon application of the magnetic field. In this system, these factors
would arise from capillary forces with the interface or steric interactions with other particles at the interface, slowing down the dynamics of the system.
To understand this phenomena, we focus on the dynamics of the particle monolayer. First, we visualize the particle monolayer of the bijels stabilized with prolate 
ellipsoids at the initial and final configuration before and after application of a magnetic field.

@@

In Figure \ref{fig:particle_viz-field_on}, we see the initial configuration of particles at the monolayer show that the orientations are random and that the 
particles tend to lie flat on the interface. However, upon application of the magnetic field the particles orient to the field direction. With no applied field,
the orientations and positions of the particles vary slightly for both ellipsoidal particle morphologies. This effect is due steric effects between particles,
as identified in Gunther et al. \cite{gunther_timescales_2014} Bijels stabilized by prolate ellipsoids, adopt orientational order
to the magnetic field and qualitatively different particle arrangements on the interface. These indicate that the interfacial capillary forces or steric interactions 
with other particles differ upon application of the magnetic field. The particles would prefer to lie flat on the interface to minimize the interfacial energy of 
adsorption onto the interface. Changes in the local arrangement arise from the unjamming and rejamming process upon application of the magnetic field. These differences 
in the orientational and interfacial ordering can be characterized to understand how each respective interaction force changes as a function of time.

Bresme and Faraudo and Davies investigating the reorientation of particles at interfaces under magnetic fields have shown that a critical magnetic field exists, 
above which the particle orients to the field and below which the particle orientation is a function of the capillary force and magnetic field derived force. 
\cite{davies_interface_2014} \cite{bresme_orientational_2007} Particle adsorption into the interface with microparticles have also been shown to be irreversible due 
to the high adsorption energy. Upon particle reorientation, the microstructure change can be driven solely through particle unjamming and re-jamming, or it can be 
driven through the particles dragging the interface during this process. The mechanism of unjamming and re-jamming can be investigated using the average interfacial 
angle, $\langle \psi \rangle$ and the local ordering of the particles characterized with  $\langle Q6 \rangle$ Past work has identified that local crystallization 
of colloidal supercooled fluids takes place at \(\langle Q6 \rangle = 0.38\). \cite{toxvaerd_role_2020} Past investigations into the rheology of bijels have revealed
that bijels are colloidal glasses percolating in 3D space. \cite{ching_bijel_2022} However, application of a magnetic field results in reorientation of particles on
the interface that can temporarily reduce the interfacial coverage of the particles on the interface, temporarily making the particle monolayer more liquid-like
than amorphous. \cite{hunter_physics_2012} Using this approximation, we can use the local crystallization result shown in Toxvaerd.

\begin{figure} 
\centering 
\includegraphics[scale=0.5]{../figures/results/paper2/interface_angle-nint-field_on.png} 
\caption{Plots of the interface angle $(\langle \psi \rangle)$ and six fold Steinhardt order parameter $(\langle Q6 \rangle)$ on the left and right respectively, 
         versus time for bijels stabilized with oblate and prolate ellipsoids on the top and bottom rows respectively. I demonstrate that upon application 
         of a magnetic field, the behavior of $(\langle \psi \rangle)$ and $(\langle Q6 \rangle)$ differ significantly between oblate and prolate ellipsoids 
         indicating that the dynamics for both particle morphologies differ. I also observe magnetic field dependence in each property for both particle types, 
         suggesting that these changes are driven primarily through the change in the applied field strength.} 
\label{fig:interface_angle-nint-field_on} 
\end{figure}

From Figure \ref{fig:interface_angle-nint-field_on}, we identify that prolate and oblate particles respond differently at the interface. For
bijels stabilized by oblate ellipsoids, we characterize an increase in $\langle \psi \rangle$ from an initial value of $19 ^{\circ}$,
before it reduces slightly and begins to increase once again. The initial starting value of $\langle \psi \rangle$ indicates the
particles are lying close to flat on the interface, before they begin to tilt out of the interface when the magnetic field is applied. Then,
$\langle \psi \rangle$ plateaus as the interface begins to move in response to the tilting particle at the interface. This is caused by the
large adsorption energy of the particles at the interface of the bijel, caused by high surface tension. Finally, the particles jam in place,
locking the interface at an angle to the particle. The rate of increase in $\langle \psi \rangle$ at early stages and the time spent
in the plateau increase with a larger applied magnetic field. The final angle at the interface is also dependent upon the applied field
strength.

When analyzing $\langle \psi \rangle$ for bijels stabilized by prolate particles, this behavior can also be observed. $\langle \psi \rangle$
begins at $10 ^{\circ}$. $\langle \psi \rangle$ increases, before plateauing and slowly decreasing. The initial peak height and rate of increase in 
$\langle \psi \rangle$ is field dependent, although given the small decrease in $\langle \psi \rangle$ it is unclear if the final value of this parameter 
is field dependent for bijels stabilized with prolate particles. The changes in $\langle \psi \rangle$ for bijels stabilized with prolate particles are 
small compared to bijels stabilized with oblate particles. We visualize this process by color coding snapshots of the particle monolayer at the initial
and final timesteps of bijels stabilized by prolate particles with a field strength of $\bar{B} = 1$ applied.

@@

From the visualizations in Figure \ref{fig:psi_field_on_visualize}, the particles lie mostly flat on the interface at the initial timestep. Upon application of a field 
strength of $\bar{B} = 1$, the final state of the monolayer is particle morphology dependent. Oblate particles tend to flip on the interface into a metastable state where
the interface covered by each particle is done with the $R_p$ and $R_o$ compared to its lowest energy state where it lies flat with radii $R_o$. The particle monolayer
of bijels stabilized by prolate particles tilt out of the interface with no metastable configurations observed. This effect explains the trends seen in $\langle \psi \rangle$
at long times for both particle morphologies. This particle flipping on the interface affects the way the particles can arrange on the interface, like what we 
characterized In Figure \ref{fig:rdf}. This change in local ordering can be quantified using $\langle Q6 \rangle$.

From Figure \ref{fig:interface_angle-nint-field_on} the dynamics of $\langle Q6 \rangle$ are particle morphology specific but can be split into three sections for 
both particle morphologies. Characterizing the time evolution of $\langle Q6 \rangle$ for oblate particles, we see a decrease upon application of the magnetic field, 
followed by a plateau and finally a gradual increase before jamming takes place, seen as a significant decrease in the rate of chang to $\langle Q6 \rangle$.
These results indicate that the ordering of the particles is reduced by the applied magnetic field, before a
restoration of some of the pre-existing order. The final values of $\langle Q6 \rangle$ are magnetic field dependent, with a stronger
magnetic field having a lower final $\langle Q6 \rangle$ value indicating that either the ordering of particles influence the angle at
the interface or vice versa.

We observe that for bijels stabilized by prolate particles, the interface ordering of the particles increases as a
function of the applied field strength. The first phase of the evolution of $\langle Q6 \rangle$ sees some growth in $\langle Q6 \rangle$ before 
increasing dramatically and plateauing as jamming takes place. The length of time of the initial plateau and growth regions are negatively and
positively correlated to the applied magnetic field strength. Upon application of the magnetic field, $\langle Q6 \rangle > 0.38$ in all cases. Approximating
the particle monolayer as a colloidal glass that underwent a glass transition, the monolayer can be said to undergo a local crystallation event when 
$\langle Q6 \rangle > 0.38$. \cite{toxvaerd_role_2020}

Thus far, three particle based phenomena have been characterized; the orientation of the particle to the magnetic field, the interface and the local 
arrangement of the particles on the interface. we can calculate a timescale for each factor from the plots of each of these properties.
The nematic order parameter $S$ represents the ordering of
particles to an average direction, which in the case of the application
of a magnetic field, is the field direction. Therefore, a timescale
reliant on the nematic order parameter would represent a timescale of
response rate limited to the response to the magnetic field, which
indicates a particle-field orientation dependence named $\tau_S$. When applying a field to a bijel system with a
randomly oriented particle monolayer, the most significant transition
point is the isotropic to nematic transition or when $S \geq 0.3$. We
define $\tau_S$ as the the isotropic to nematic transition point.

We can also do the same for $\langle \psi \rangle$ and
$\langle Q6 \rangle$. A timescale derived from
$\langle \psi \rangle$ named $\tau_{\langle \psi \rangle}$
represents the capillary timescale between the interface and the
particle. Given the shape of the plot, we assign
$\tau_{\langle \psi \rangle}$ to be the time when the first minimum of
$\langle \psi \rangle$ is observed for prolate particles and the first
maximum for oblate particles. A timescale derived from
$\langle Q6 \rangle$, named $\tau_{\langle Q6 \rangle}$ is also
calculated which represents a timescale of local particle rearrangement.
We define $\tau_{\langle Q6 \rangle}$ as the time when
\(\langle Q6 \rangle \geq 0.38\) for prolate particles and the global
minimum of $\tau_{\langle Q6 \rangle}$ for the oblate particles. I
omit \(\bar{B} = 0\) as previous results have identified the domain size
changes observed there. We then plot the average domain size $L$
against time rescaled with these three timescales in Figure
\ref{fig:domain_size-field_on-scaled}.

@@

The right plot demonstrates the domain size change after rescaling time
with $\tau_{\langle Q6 \rangle}$ all plots collapse onto a single line and 
the domain size transition also begins at
$\frac{t}{\tau_{\langle Q6 \rangle}} = 1$. The latter point
demonstrates that the dynamics for the structural response of randomly
oriented particles are controlled by the local particle rearrangement at
the interface rather than the orientation of the particle to the
magnetic field. As the dynamics of both particle morphologies are well described
using the particle steric effects timescale, denoted by $\tau_{\langle Q6 \rangle}$,
We conclude that the dynamics of bijels stabilized by ellipsoidal particles are controlled by
interfacial particle rearrangement at the interface.

@@

Bijels are kinetically stable structures whose properties are dependent
upon the stability of the particle monolayer. Past work into responsive
emulsions have demonstrated resilience to microstructure changes after
application and removal of stimuli even after several months. \cite{cui_stabilizing_2013} However,
in the systems simulated above the particles need not necessarily be in
thermodynamically stable states when jammed upon removal of stimuli as
the particles take up a arrangements not observed when no field is
applied. In this section, we explore how removal of the magnetic field
changes the microstructure of the bijel as a function of the initial
particle order. We use bijels simulated under
$\bar{B}_{template} = 0, 0.2, 0.5, 1$ during formation of the bijel. Once
the microstructure has stabilized, we switch off the magnetic field and
observe the time evolution of the system for $t = 10^5$ timesteps.
